
Research Findings:
This section has been split into nine sections to simplify the comparison of the different materials, and the respective manufacturing workflows associated with them, as well as the properties of the materials themselves. The nine sections are as follows:

\begin{itemize}[itemsep=2mm]
    \item Tensile Strength
    \item Elasticity
    \item Surface Quality
    \item Thermal Properties
    \item Precision
    \item Cost
    \item Time Consumption
    \item Complexity in Manufacturing Process
    \item Environmental Impact
\end{itemize}


\section{Tensile Strength}

    A key attribute that determines a material's capacity to resist pulling forces without breaking is its
    tensile strength. A number of differences were found when 3D-printed PLA (polylactic acid) and 6061-T6 aluminum were compared, emphasizing the distinctive mechanical properties of each material.

    PLA is a bioplastic composed of renewable resources like corn starch and from a technical data sheet
    made by BCN3D Technologies, an ultimate tensile strength of 70 MPa was reported from them. %(link) 
    The value shown is the highest possible stress PLA can withstand before breaking down to tension. Due to
    PLA has a relatively lower tensile strength, being a polymer and having a layer-by-layer deposition while 3D printing, can result in the formation of weak areas along the contact points. Despite its lower
    tensile strength compared to metals, PLA can be used in situations where mechanical strength is not as important and instead can be used when specified components have to be made. Examples of what
    components were made through 3D printing are shown below.
    
    %[insert images of Chassis Body Corners, Suspension Rocker & Boogie, Chassis-Rocker Connector]

    On the other hand, according to a material data sheet published by ASM International %(link)
    , 6061-T6 aluminum, a commonly used alloy in several industrial applications, showed a significantly greater
    ultimate tensile strength of 310 MPa. The composition of the alloy and the T6 tempering process, which
    includes heat treatment and artificial aging to improve the mechanical properties of the alloy, is responsible for its high tensile strength. For structural components and applications that need high
    amounts of strength, 6061-T6 aluminum is the ideal material due to its better tensile strength. A good
    example can be the motor-wheel shaft which transmits torque from the motor to the wheel hub and from
    the wheel hub to the wheel. In addition, there is the motor cover which supports the weight of the rover.
    This can be shown below.

    %[insert images of Shaft and Motor Cover working (can be an image from Fusion360)]

    The wide range in tensile strength between PLA and 6061-T6 aluminum shows the need for choosing a material according to the particular requirements of a given application. PLA has advantages in terms of
    manufacturing and environmental impact (mentioned in Section ….), but its mechanical limits restrict its
    application to less demanding structural tasks. Whereas, when mechanical strength is crucial, 6061-T6
    aluminum's durability and reliability make it essential. This comparison emphasizes how important it is
    for engineering and industrial projects to consider both mechanical qualities and application requirements when choosing materials.

\section{Elasticity}

    The Young's Modulus and Elasticity between PLA and 6061-T6 aluminum showed differences when
    compared to one another, which suggests their different uses and stress resistance.
    
    Based on BCN3D Technologies' datasheet o PLA (link), the material has a Young's modulus of 3120 MPa (or
    roughly 3.2 GPa). The fact that PLA is a semi-crystalline polymer that was intended to be flexible and
    simple to produce can be seen in its low modulus score (link). The elasticity of PLA was moderate,
    meaning that it could deform under stress and return to its former shape when the load was released.

    However, with certain components, the 3D-printed PLA could make it brittle. Therefore, it was appropriate
    for low-stress applications and prototyping where high rigidity was not a requirement. Elasticity in a
    material helped so that it could absorb some impact without permanent deformation, making it useful for
    lightweight and less structurally demanding parts.
    6061-T6 aluminum had a much greater Young's modulus of 68.9 GPa (link). Compared to PLA, 6061-T6
    aluminum was stiffer and had a smaller chance to deform under stress, as shown by its higher modulus.

    The material was applicable in instances where rigidity and endurance were required due to its
    decreased elasticity, which allowed it to bear larger loads without experiencing significant deformation.
    The contrast in elasticity and Young's modulus between PLA and 6061-T6 aluminum showed the different
    uses for which each material was appropriate. PLA was made for the use of rapid prototyping and
    scenarios where it required some flexibility because of its lower modulus and increased elasticity.
    Whereas with 6061-T6 aluminum's higher modulus and low elasticity, it made it useful in high-stress
    situations where strength and durability were expected.
